<!-- 
save as 'sgRNAChild.Rmd'
child of 'sgRNA.Rmd'
--> 

```{r, results='asis', eval=gseBool[counter]}
enrichment <- geneList$GSE[[counter]]
cat("##", paste(enrichment$genes, collapse = ", "), sprintf("(%s)", counter))
```

### Pathways

The following pathway databases were accessed:
[WikiPathways 2016](http://www.wikipathways.org/index.php/Download_Pathways), 
[KEGG 2016](http://www.kegg.jp/kegg/download/), 
[Biocarta 2016](https://cgap.nci.nih.gov/Pathways/BioCarta_Pathways), 
[Reactome 2016](http://www.reactome.org/pages/download-data/), 
[NCI-Nature 2016](https://wiki.nci.nih.gov/pages/viewpage.action?pageId=315491760), 
[Panther 2016](http://www.pantherdb.org/pathway/).
The results are shown below as graphs and tabulars for each database.

#### Wiki Pathways

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "WikiPathways_2016")
  
  tt <- tagList(
    shiny::tags$strong("{point.name}"), shiny::tags$br(),
    shiny::tags$div("Score : {point.y:.5f}", shiny::tags$br(),
                    shiny::tags$div("Adjusted P-Value : {point.qval:.5f}"), shiny::tags$br(),
                    shiny::tags$div("Genes associated: {point.genes}")
    )
  ) %>% as.character()
  
  if(nrow(filtered) == 0)
  {
    Plot_blank(device="hc", msg = "No data available")
  } else {
    # Create Highcharter plot
    Plot_bar( seriesNames = c("score"),
              catName = "category",
              data = filtered, 
              tooltip = tt,
              title = "Wiki Pathways",
              subtitle = "Gene Set Enrichment",
              xLab = "Score",
              yLab = "Annotation",
              zoom = "x",
              crosshair = TRUE, legend = TRUE, export = TRUE, cols = NULL, anno = NULL, col = NULL, filename = "WikiPathways_2016" )
  }
```


```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "WikiPathways_2016")
  
  Table_DT(filtered, colNames = c("Database", "Term", "P-Value", "Adjusted P-Value", "Z-Score", "EnrichR Score", "Involved Genes"), bRownames = FALSE, style = "default", class = "display", 
           dom = "flrtip", alignment = list(centre = NULL, justify = NULL, left = NULL), 
           formatCurr = NULL, formatPerc = NULL, formatRoun = list("cols" = c(3,4,5,6), "digits" = 4), buttons = c('copy', 'csv', 'excel', 'pdf', 'print'), bResponsive = FALSE,
           pageLen = 5, bScroll = FALSE, filename = "GeneSetEnrichment_WikiPathways_2016" )
```


#### KEGG

```{r}
  filtered <-  dplyr::filter(enrichment$enrichr, database == "KEGG_2016")
  
  tt <- tagList(
    shiny::tags$strong("{point.name}"), shiny::tags$br(),
    shiny::tags$div("Score : {point.y:.5f}", shiny::tags$br(),
                    shiny::tags$div("Adjusted P-Value : {point.qval:.5f}"), shiny::tags$br(),
                    shiny::tags$div("Genes associated: {point.genes}")
    )
  ) %>% as.character()
  
  if(nrow(filtered) == 0)
  {
    Plot_blank(device="hc", msg = "No data available")
  } else {
    # Create Highcharter plot
    Plot_bar( seriesNames = c("score"),
              catName = "category",
              data = filtered, 
              tooltip = tt,
              title = "KEGG",
              subtitle = "Gene Set Enrichment",
              xLab = "Score",
              yLab = "Annotation",
              zoom = "x",
              crosshair = TRUE, legend = TRUE, export = TRUE, cols = NULL, anno = NULL, col = NULL, filename = "KEGG_2016" )
  }
```

```{r}
  filtered <-  dplyr::filter(enrichment$enrichr, database == "KEGG_2016")
  
  Table_DT(filtered, colNames = c("Database", "Term", "P-Value", "Adjusted P-Value", "Z-Score", "EnrichR Score", "Involved Genes"), bRownames = FALSE, style = "default", class = "display", 
           dom = "flrtip", alignment = list(centre = NULL, justify = NULL, left = NULL), 
           formatCurr = NULL, formatPerc = NULL, formatRoun = list("cols" = c(3,4,5,6), "digits" = 4), buttons = c('copy', 'csv', 'excel', 'pdf', 'print'), bResponsive = FALSE,
           pageLen = 5, bScroll = FALSE, filename = "GeneSetEnrichment_KEGG_2016" )
```


#### Biocarta

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "Biocarta_2016")
  
  tt <- tagList(
    shiny::tags$strong("{point.name}"), shiny::tags$br(),
    shiny::tags$div("Score : {point.y:.5f}", shiny::tags$br(),
                    shiny::tags$div("Adjusted P-Value : {point.qval:.5f}"), shiny::tags$br(),
                    shiny::tags$div("Genes associated: {point.genes}")
    )
  ) %>% as.character()
  
  if(nrow(filtered) == 0)
  {
    Plot_blank(device="hc", msg = "No data available")
  } else {
    # Create Highcharter plot
    Plot_bar( seriesNames = c("score"),
              catName = "category",
              data = filtered, 
              tooltip = tt,
              title = "Biocarta",
              subtitle = "Gene Set Enrichment",
              xLab = "Score",
              yLab = "Annotation",
              zoom = "x",
              crosshair = TRUE, legend = TRUE, export = TRUE, cols = NULL, anno = NULL, col = NULL, filename = "Biocarta_2016" )
  }
```


```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "Biocarta_2016")
  
  Table_DT(filtered, colNames = c("Database", "Term", "P-Value", "Adjusted P-Value", "Z-Score", "EnrichR Score", "Involved Genes"), bRownames = FALSE, style = "default", class = "display", 
           dom = "flrtip", alignment = list(centre = NULL, justify = NULL, left = NULL), 
           formatCurr = NULL, formatPerc = NULL, formatRoun = list("cols" = c(3,4,5,6), "digits" = 4), buttons = c('copy', 'csv', 'excel', 'pdf', 'print'), bResponsive = FALSE,
           pageLen = 5, bScroll = FALSE, filename = "GeneSetEnrichment_Biocarta_2016" )
```


#### Reactome

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "Reactome_2016")
  
  tt <- tagList(
    shiny::tags$strong("{point.name}"), shiny::tags$br(),
    shiny::tags$div("Score : {point.y:.5f}", shiny::tags$br(),
                    shiny::tags$div("Adjusted P-Value : {point.qval:.5f}"), shiny::tags$br(),
                    shiny::tags$div("Genes associated: {point.genes}")
    )
  ) %>% as.character()
  
  if(nrow(filtered) == 0)
  {
    Plot_blank(device="hc", msg = "No data available")
  } else {
    # Create Highcharter plot
    Plot_bar( seriesNames = c("score"),
              catName = "category",
              data = filtered, 
              tooltip = tt,
              title = "Reactome",
              subtitle = "Gene Set Enrichment",
              xLab = "Score",
              yLab = "Annotation",
              zoom = "x",
              crosshair = TRUE, legend = TRUE, export = TRUE, cols = NULL, anno = NULL, col = NULL, filename = "Reactome_2016" )
  }
```

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "Reactome_2016")
  
  Table_DT(filtered, colNames = c("Database", "Term", "P-Value", "Adjusted P-Value", "Z-Score", "EnrichR Score", "Involved Genes"), bRownames = FALSE, style = "default", class = "display", 
           dom = "flrtip", alignment = list(centre = NULL, justify = NULL, left = NULL), 
           formatCurr = NULL, formatPerc = NULL, formatRoun = list("cols" = c(3,4,5,6), "digits" = 4), buttons = c('copy', 'csv', 'excel', 'pdf', 'print'), bResponsive = FALSE,
           pageLen = 5, bScroll = FALSE, filename = "GeneSetEnrichment_Reactome_2016" )
```


#### NCI Nature 2016

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "NCI-Nature_2016")
  
  tt <- tagList(
    shiny::tags$strong("{point.name}"), shiny::tags$br(),
    shiny::tags$div("Score : {point.y:.5f}", shiny::tags$br(),
                    shiny::tags$div("Adjusted P-Value : {point.qval:.5f}"), shiny::tags$br(),
                    shiny::tags$div("Genes associated: {point.genes}")
    )
  ) %>% as.character()
  
  if(nrow(filtered) == 0)
  {
    Plot_blank(device="hc", msg = "No data available")
  } else {
    # Create Highcharter plot
    Plot_bar( seriesNames = c("score"),
              catName = "category",
              data = filtered, 
              tooltip = tt,
              title = "NCI Nature",
              subtitle = "Gene Set Enrichment",
              xLab = "Score",
              yLab = "Annotation",
              zoom = "x",
              crosshair = TRUE, legend = TRUE, export = TRUE, cols = NULL, anno = NULL, col = NULL, filename = "NCI-Nature_2016" )
  }
```

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "NCI-Nature_2016")
  
  Table_DT(filtered, colNames = c("Database", "Term", "P-Value", "Adjusted P-Value", "Z-Score", "EnrichR Score", "Involved Genes"), bRownames = FALSE, style = "default", class = "display", 
           dom = "flrtip", alignment = list(centre = NULL, justify = NULL, left = NULL), 
           formatCurr = NULL, formatPerc = NULL, formatRoun = list("cols" = c(3,4,5,6), "digits" = 4), buttons = c('copy', 'csv', 'excel', 'pdf', 'print'), bResponsive = FALSE,
           pageLen = 5, bScroll = FALSE, filename = "GeneSetEnrichment_NCI-Nature_2016" )
```


#### Panther 2016

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "Panther_2016")
  
  tt <- tagList(
    shiny::tags$strong("{point.name}"), shiny::tags$br(),
    shiny::tags$div("Score : {point.y:.5f}", shiny::tags$br(),
                    shiny::tags$div("Adjusted P-Value : {point.qval:.5f}"), shiny::tags$br(),
                    shiny::tags$div("Genes associated: {point.genes}")
    )
  ) %>% as.character()
  
  if(nrow(filtered) == 0)
  {
    Plot_blank(device="hc", msg = "No data available")
  } else {
    # Create Highcharter plot
    Plot_bar( seriesNames = c("score"),
              catName = "category",
              data = filtered, 
              tooltip = tt,
              title = "Panther",
              subtitle = "Gene Set Enrichment",
              xLab = "Score",
              yLab = "Annotation",
              zoom = "x",
              crosshair = TRUE, legend = TRUE, export = TRUE, cols = NULL, anno = NULL, col = NULL, filename = "Panther_2016" )
  }
```

```{r}
Table_DT(filtered, colNames = c("Database", "Term", "P-Value", "Adjusted P-Value", "Z-Score", "EnrichR Score", "Involved Genes"), bRownames = FALSE, style = "default", class = "display", 
           dom = "flrtip", alignment = list(centre = NULL, justify = NULL, left = NULL), 
           formatCurr = NULL, formatPerc = NULL, formatRoun = list("cols" = c(3,4,5,6), "digits" = 4), buttons = c('copy', 'csv', 'excel', 'pdf', 'print'), bResponsive = FALSE,
           pageLen = 5, bScroll = FALSE, filename = "GeneSetEnrichment_NCI-Panther_2016" )
```














<br/><br/>

### Transcription

Gene Set Analysis was performed using different databases for transcriptional information provided by the Enrichr service.
The following databases were accessed:
[ChEA 2015](http://amp.pharm.mssm.edu/lib/cheadownload.jsp), 
[TRANSFAC and JASPAR PWMs](http://jaspar.genereg.net/), 
[ENCODE and ChEA Consensus TFs from ChIP-X](http://amp.pharm.mssm.edu/Enrichr/geneSetLibrary?mode=text&libraryName=ENCODE_and_ChEA_Consensus_TFs_from_ChIP-X), 
[TargetScan microRNA Targets](http://www.targetscan.org/cgi-bin/targetscan/data_download.cgi?db=vert_61), 
[Transcription Factor PPIs](http://amp.pharm.mssm.edu/Enrichr/geneSetLibrary?mode=text&libraryName=Transcription_Factor_PPIs).
The results are shown below as graphs and tabulars for each database.

#### ChEA 2015 Data

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "ChEA_2015")

  tt <- tagList(
    shiny::tags$strong("{point.name}"), shiny::tags$br(),
    shiny::tags$div("Score : {point.y:.5f}", shiny::tags$br(),
                    shiny::tags$div("Adjusted P-Value : {point.qval:.5f}"), shiny::tags$br(),
                    shiny::tags$div("Genes associated: {point.genes}")
    )
  ) %>% as.character()
  
  if(nrow(filtered) == 0)
  {
     Plot_blank(device="hc", msg = "No data available")
  } else {
    # Create Highcharter plot
    Plot_bar( seriesNames = c("score"),
              catName = "category",
              data = filtered, 
              tooltip = tt,
              title = "ChEA 2015",
              subtitle = "Gene Set Enrichment",
              xLab = "Score",
              yLab = "Annotation",
              zoom = "x",
              crosshair = TRUE, legend = TRUE, export = TRUE, cols = NULL, anno = NULL, col = NULL, filename = "GeneSetEnrichment_ChEA_2015" )
  }
```

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "ChEA_2015")
  
  Table_DT(filtered, colNames = c("Database", "Term", "P-Value", "Adjusted P-Value", "Z-Score", "EnrichR Score", "Involved Genes"), bRownames = FALSE, style = "default", class = "display", 
          dom = "flrtip", alignment = list(centre = NULL, justify = NULL, left = NULL), 
          formatCurr = NULL, formatPerc = NULL, formatRoun = list("cols" = c(3,4,5,6), "digits" = 4), buttons = c('copy', 'csv', 'excel', 'pdf', 'print'), bResponsive = FALSE,
          pageLen = 5, bScroll = FALSE, filename = "GeneSetEnrichment_ChEA_2015" )
```


#### TRANSFAC and JASPAR PWMs

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "TRANSFAC_and_JASPAR_PWMs")
  
  tt <- tagList(
    shiny::tags$strong("{point.name}"), shiny::tags$br(),
    shiny::tags$div("Score : {point.y:.5f}", shiny::tags$br(),
                    shiny::tags$div("Adjusted P-Value : {point.qval:.5f}"), shiny::tags$br(),
                    shiny::tags$div("Genes associated: {point.genes}")
    )
  ) %>% as.character()
  
  if(nrow(filtered) == 0)
  {
    Plot_blank(device="hc", msg = "No data available")
  } else {
    # Create Highcharter plot
    Plot_bar( seriesNames = c("score"),
              catName = "category",
              data = filtered, 
              tooltip = tt,
              title = "TRANSFAC and JASPAR",
              subtitle = "Gene Set Enrichment",
              xLab = "Score",
              yLab = "Annotation",
              zoom = "x",
              crosshair = TRUE, legend = TRUE, export = TRUE, cols = NULL, anno = NULL, col = NULL, filename = "GeneSetEnrichment_TRANSFAC_and_JASPAR_PWMs" )
  }
```

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "TRANSFAC_and_JASPAR_PWMs")
  
  Table_DT(filtered, colNames = c("Database", "Term", "P-Value", "Adjusted P-Value", "Z-Score", "EnrichR Score", "Involved Genes"), bRownames = FALSE, style = "default", class = "display", 
           dom = "flrtip", alignment = list(centre = NULL, justify = NULL, left = NULL), 
           formatCurr = NULL, formatPerc = NULL, formatRoun = list("cols" = c(3,4,5,6), "digits" = 4), buttons = c('copy', 'csv', 'excel', 'pdf', 'print'), bResponsive = FALSE,
           pageLen = 5, bScroll = FALSE, filename = "GeneSetEnrichment_TRANSFAC_and_JASPAR_PWMs" )
```



#### ENCODE and ChEA Consensus TFs from ChIP-X

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "ENCODE_and_ChEA_Consensus_TFs_from_ChIP-X")
  
  tt <- tagList(
    shiny::tags$strong("{point.name}"), shiny::tags$br(),
    shiny::tags$div("Score : {point.y:.5f}", shiny::tags$br(),
                    shiny::tags$div("Adjusted P-Value : {point.qval:.5f}"), shiny::tags$br(),
                    shiny::tags$div("Genes associated: {point.genes}")
    )
  ) %>% as.character()
  
  if(nrow(filtered) == 0)
  {
    Plot_blank(device="hc", msg = "No data available")
  } else {
    # Create Highcharter plot
    Plot_bar( seriesNames = c("score"),
              catName = "category",
              data = filtered, 
              tooltip = tt,
              title = "ENCODE and ChEA Transcription Factor ChIP-X",
              subtitle = "Gene Set Enrichment",
              xLab = "Score",
              yLab = "Annotation",
              zoom = "x",
              crosshair = TRUE, legend = TRUE, export = TRUE, cols = NULL, anno = NULL, col = NULL, filename = "GeneSetEnrichment_ENCODE_and_ChEA_Consensus_TFs_from_ChIP-X" )
  }
```

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "ENCODE_and_ChEA_Consensus_TFs_from_ChIP-X")
  
  Table_DT(filtered, colNames = c("Database", "Term", "P-Value", "Adjusted P-Value", "Z-Score", "EnrichR Score", "Involved Genes"), bRownames = FALSE, style = "default", class = "display", 
           dom = "flrtip", alignment = list(centre = NULL, justify = NULL, left = NULL), 
           formatCurr = NULL, formatPerc = NULL, formatRoun = list("cols" = c(3,4,5,6), "digits" = 4), buttons = c('copy', 'csv', 'excel', 'pdf', 'print'), bResponsive = FALSE,
           pageLen = 5, bScroll = FALSE, filename = "GeneSetEnrichment_ENCODE_and_ChEA_Consensus_TFs_from_ChIP-X" )
```



#### TargetScan microRNA

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "TargetScan_microRNA")
  
  tt <- tagList(
    shiny::tags$strong("{point.name}"), shiny::tags$br(),
    shiny::tags$div("Score : {point.y:.5f}", shiny::tags$br(),
                    shiny::tags$div("Adjusted P-Value : {point.qval:.5f}"), shiny::tags$br(),
                    shiny::tags$div("Genes associated: {point.genes}")
    )
  ) %>% as.character()
  
  if(nrow(filtered) == 0)
  {
    Plot_blank(device="hc", msg = "No data available")
  } else {
    # Create Highcharter plot
    Plot_bar( seriesNames = c("score"),
              catName = "category",
              data = filtered, 
              tooltip = tt,
              title = "TargetScan microRNA",
              subtitle = "Gene Set Enrichment",
              xLab = "Score",
              yLab = "Annotation",
              zoom = "x",
              crosshair = TRUE, legend = TRUE, export = TRUE, cols = NULL, anno = NULL, col = NULL, filename = "TargetScan_microRNA" )
  }
```

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "TargetScan_microRNA")
  
  Table_DT(filtered, colNames = c("Database", "Term", "P-Value", "Adjusted P-Value", "Z-Score", "EnrichR Score", "Involved Genes"), bRownames = FALSE, style = "default", class = "display", 
           dom = "flrtip", alignment = list(centre = NULL, justify = NULL, left = NULL), 
           formatCurr = NULL, formatPerc = NULL, formatRoun = list("cols" = c(3,4,5,6), "digits" = 4), buttons = c('copy', 'csv', 'excel', 'pdf', 'print'), bResponsive = FALSE,
           pageLen = 5, bScroll = FALSE, filename = "GeneSetEnrichment_TargetScan_microRNA" )
```



#### Transcription Factor PPIs

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "Transcription_Factor_PPIs")
  
  tt <- tagList(
    shiny::tags$strong("{point.name}"), shiny::tags$br(),
    shiny::tags$div("Score : {point.y:.5f}", shiny::tags$br(),
                    shiny::tags$div("Adjusted P-Value : {point.qval:.5f}"), shiny::tags$br(),
                    shiny::tags$div("Genes associated: {point.genes}")
    )
  ) %>% as.character()
  
  if(nrow(filtered) == 0)
  {
    Plot_blank(device="hc", msg = "No data available")
  } else {
    # Create Highcharter plot
    Plot_bar( seriesNames = c("score"),
              catName = "category",
              data = filtered, 
              tooltip = tt,
              title = "Transcription Factor Interactions",
              subtitle = "Gene Set Enrichment",
              xLab = "Score",
              yLab = "Annotation",
              zoom = "x",
              crosshair = TRUE, legend = TRUE, export = TRUE, cols = NULL, anno = NULL, col = NULL, filename = "Transcription_Factor_PPIs" )
  }
```

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "Transcription_Factor_PPIs")
  
  Table_DT(filtered, colNames = c("Database", "Term", "P-Value", "Adjusted P-Value", "Z-Score", "EnrichR Score", "Involved Genes"), bRownames = FALSE, style = "default", class = "display", 
           dom = "flrtip", alignment = list(centre = NULL, justify = NULL, left = NULL), 
           formatCurr = NULL, formatPerc = NULL, formatRoun = list("cols" = c(3,4,5,6), "digits" = 4), buttons = c('copy', 'csv', 'excel', 'pdf', 'print'), bResponsive = FALSE,
           pageLen = 5, bScroll = FALSE, filename = "GeneSetEnrichment_Transcription_Factor_PPIs" )
```




















<br/><br/>

### Ontologies

Enrichr was used to retrieve a Gene Ontology Gene set analysis from the Gene Ontology Consortium.
The following databases were accessed:
[GO Biological Process 2015](http://www.geneontology.org/page/download-annotations), 
[GO Cellular Component 2015](http://www.geneontology.org/page/download-annotations), 
[GO Molecular Function 2015](http://www.geneontology.org/page/download-annotations).
The results are shown below as graphs and tabulars for each database.

#### GO Biological Process

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "GO_Biological_Process_2015")
  
  tt <- tagList(
    shiny::tags$strong("{point.name}"), shiny::tags$br(),
    shiny::tags$div("Score : {point.y:.5f}", shiny::tags$br(),
                    shiny::tags$div("Adjusted P-Value : {point.qval:.5f}"), shiny::tags$br(),
                    shiny::tags$div("Genes associated: {point.genes}")
    )
  ) %>% as.character()
  
  if(nrow(filtered) == 0)
  {
    Plot_blank(device="hc", msg = "No data available")
  } else {
    # Create Highcharter plot
    Plot_bar( seriesNames = c("score"),
              catName = "category",
              data = filtered, 
              tooltip = tt,
              title = "GO Biological Process 2015",
              subtitle = "Gene Set Enrichment",
              xLab = "Score",
              yLab = "Annotation",
              zoom = "x",
              crosshair = TRUE, legend = TRUE, export = TRUE, cols = NULL, anno = NULL, col = NULL, filename = "GO_Biological_Process_2015" )
  }
```

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "GO_Biological_Process_2015")
  
  Table_DT(filtered, colNames = c("Database", "Term", "P-Value", "Adjusted P-Value", "Z-Score", "EnrichR Score", "Involved Genes"), bRownames = FALSE, style = "default", class = "display", 
           dom = "flrtip", alignment = list(centre = NULL, justify = NULL, left = NULL), 
           formatCurr = NULL, formatPerc = NULL, formatRoun = list("cols" = c(3,4,5,6), "digits" = 4), buttons = c('copy', 'csv', 'excel', 'pdf', 'print'), bResponsive = FALSE,
           pageLen = 5, bScroll = FALSE, filename = "GeneSetEnrichment_GO_Biological_Process_2015" )
```



#### GO Molecular Function

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "GO_Molecular_Function_2015")
  
  tt <- tagList(
    shiny::tags$strong("{point.name}"), shiny::tags$br(),
    shiny::tags$div("Score : {point.y:.5f}", shiny::tags$br(),
                    shiny::tags$div("Adjusted P-Value : {point.qval:.5f}"), shiny::tags$br(),
                    shiny::tags$div("Genes associated: {point.genes}")
    )
  ) %>% as.character()
  
  if(nrow(filtered) == 0)
  {
    Plot_blank(device="hc", msg = "No data available")
  } else {
    # Create Highcharter plot
    Plot_bar( seriesNames = c("score"),
              catName = "category",
              data = filtered, 
              tooltip = tt,
              title = "GO Molecular Function 2015",
              subtitle = "Gene Set Enrichment",
              xLab = "Score",
              yLab = "Annotation",
              zoom = "x",
              crosshair = TRUE, legend = TRUE, export = TRUE, cols = NULL, anno = NULL, col = NULL, filename = "GO_Molecular_Function_2015" )
  }
```

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "GO_Molecular_Function_2015")
  
  Table_DT(filtered, colNames = c("Database", "Term", "P-Value", "Adjusted P-Value", "Z-Score", "EnrichR Score", "Involved Genes"), bRownames = FALSE, style = "default", class = "display", 
           dom = "flrtip", alignment = list(centre = NULL, justify = NULL, left = NULL), 
           formatCurr = NULL, formatPerc = NULL, formatRoun = list("cols" = c(3,4,5,6), "digits" = 4), buttons = c('copy', 'csv', 'excel', 'pdf', 'print'), bResponsive = FALSE,
           pageLen = 5, bScroll = FALSE, filename = "GeneSetEnrichment_GO_Molecular_Function_2015" )
```



#### GO Cellular Component

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "GO_Cellular_Component_2015")
  
  tt <- tagList(
    shiny::tags$strong("{point.name}"), shiny::tags$br(),
    shiny::tags$div("Score : {point.y:.5f}", shiny::tags$br(),
                    shiny::tags$div("Adjusted P-Value : {point.qval:.5f}"), shiny::tags$br(),
                    shiny::tags$div("Genes associated: {point.genes}")
    )
  ) %>% as.character()
  
  if(nrow(filtered) == 0)
  {
    Plot_blank(device="hc", msg = "No data available")
  } else {
    # Create Highcharter plot
    Plot_bar( seriesNames = c("score"),
              catName = "category",
              data = filtered, 
              tooltip = tt,
              title = "GO Cellular Component 2015",
              subtitle = "Gene Set Enrichment",
              xLab = "Score",
              yLab = "Annotation",
              zoom = "x",
              crosshair = TRUE, legend = TRUE, export = TRUE, cols = NULL, anno = NULL, col = NULL, filename = "GO_Cellular_Component_2015" )
  }
```

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "GO_Cellular_Component_2015")
  
  Table_DT(filtered, colNames = c("Database", "Term", "P-Value", "Adjusted P-Value", "Z-Score", "EnrichR Score", "Involved Genes"), bRownames = FALSE, style = "default", class = "display", 
           dom = "flrtip", alignment = list(centre = NULL, justify = NULL, left = NULL), 
           formatCurr = NULL, formatPerc = NULL, formatRoun = list("cols" = c(3,4,5,6), "digits" = 4), buttons = c('copy', 'csv', 'excel', 'pdf', 'print'), bResponsive = FALSE,
           pageLen = 5, bScroll = FALSE, filename = "GeneSetEnrichment_GO_Cellular_Component_2015" )
```



















<br/><br/>

### Diseases

Enrichr was used to retrieve data from the Online Mendelian Inheritance in Man Database.
The [OMIM](http://www.omim.org/) database wwas accessed.
The results are shown below as graphs and tabulars.

#### OMIM Diseases

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "OMIM_Disease")
  
  tt <- tagList(
    shiny::tags$strong("{point.name}"), shiny::tags$br(),
    shiny::tags$div("Score : {point.y:.5f}", shiny::tags$br(),
                    shiny::tags$div("Adjusted P-Value : {point.qval:.5f}"), shiny::tags$br(),
                    shiny::tags$div("Genes associated: {point.genes}")
    )
  ) %>% as.character()
  
  if(nrow(filtered) == 0)
  {
    Plot_blank(device="hc", msg = "No data available")
  } else {
    # Create Highcharter plot
    Plot_bar( seriesNames = c("score"),
              catName = "category",
              data = filtered, 
              tooltip = tt,
              title = "OMIM Disease",
              subtitle = "Gene Set Enrichment",
              xLab = "Score",
              yLab = "Annotation",
              zoom = "x",
              crosshair = TRUE, legend = TRUE, export = TRUE, cols = NULL, anno = NULL, col = NULL, filename = "OMIM_Disease" )
  }
```

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "OMIM_Disease")
  
  Table_DT(filtered, colNames = c("Database", "Term", "P-Value", "Adjusted P-Value", "Z-Score", "EnrichR Score", "Involved Genes"), bRownames = FALSE, style = "default", class = "display", 
           dom = "flrtip", alignment = list(centre = NULL, justify = NULL, left = NULL), 
           formatCurr = NULL, formatPerc = NULL, formatRoun = list("cols" = c(3,4,5,6), "digits" = 4), buttons = c('copy', 'csv', 'excel', 'pdf', 'print'), bResponsive = FALSE,
           pageLen = 5, bScroll = FALSE, filename = "GeneSetEnrichment_OMIM_Disease" )
```



















<br/><br/>

### Cell Types

Enrichr was used to retrieve genetic information about cell lines.
The following databases were accessed:
[Cancer Cell Line Encyclopedia](https://portals.broadinstitute.org/ccle/data/browseData), 
[NCI-60 Cancer Cell Lines](http://biogps.org/downloads/).
The results are shown below as graphs and tabulars for each database.

#### Cancer Cell Line Encyclopedia

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "Cancer_Cell_Line_Encyclopedia")
  
  tt <- tagList(
    shiny::tags$strong("{point.name}"), shiny::tags$br(),
    shiny::tags$div("Score : {point.y:.5f}", shiny::tags$br(),
                    shiny::tags$div("Adjusted P-Value : {point.qval:.5f}"), shiny::tags$br(),
                    shiny::tags$div("Genes associated: {point.genes}")
    )
  ) %>% as.character()
  
  if(nrow(filtered) == 0)
  {
    Plot_blank(device="hc", msg = "No data available")
  } else {
    # Create Highcharter plot
    Plot_bar( seriesNames = c("score"),
              catName = "category",
              data = filtered, 
              tooltip = tt,
              title = "Cancer Cell Line Encyclopedia",
              subtitle = "Gene Set Enrichment",
              xLab = "Score",
              yLab = "Annotation",
              zoom = "x",
              crosshair = TRUE, legend = TRUE, export = TRUE, cols = NULL, anno = NULL, col = NULL, filename = "Cancer_Cell_Line_Encyclopedia" )
  }
```

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "Cancer_Cell_Line_Encyclopedia")
  
  Table_DT(filtered, colNames = c("Database", "Term", "P-Value", "Adjusted P-Value", "Z-Score", "EnrichR Score", "Involved Genes"), bRownames = FALSE, style = "default", class = "display", 
           dom = "flrtip", alignment = list(centre = NULL, justify = NULL, left = NULL), 
           formatCurr = NULL, formatPerc = NULL, formatRoun = list("cols" = c(3,4,5,6), "digits" = 4), buttons = c('copy', 'csv', 'excel', 'pdf', 'print'), bResponsive = FALSE,
           pageLen = 5, bScroll = FALSE, filename = "GeneSetEnrichment_Cancer_Cell_Line_Encyclopedia" )
```



#### NCI-60 Cancer Cell Line Panel

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "NCI-60_Cancer_Cell_Lines")
  
  tt <- tagList(
    shiny::tags$strong("{point.name}"), shiny::tags$br(),
    shiny::tags$div("Score : {point.y:.5f}", shiny::tags$br(),
                    shiny::tags$div("Adjusted P-Value : {point.qval:.5f}"), shiny::tags$br(),
                    shiny::tags$div("Genes associated: {point.genes}")
    )
  ) %>% as.character()
  
  if(nrow(filtered) == 0)
  {
    Plot_blank(device="hc", msg = "No data available")
  } else {
    # Create Highcharter plot
    Plot_bar( seriesNames = c("score"),
              catName = "category",
              data = filtered, 
              tooltip = tt,
              title = "NCI-60 Cancer Cell Lines",
              subtitle = "Gene Set Enrichment",
              xLab = "Score",
              yLab = "Annotation",
              zoom = "x",
              crosshair = TRUE, legend = TRUE, export = TRUE, cols = NULL, anno = NULL, col = NULL, filename = "NCI-60_Cancer_Cell_Lines" )
  }
```

```{r}
filtered <-  dplyr::filter(enrichment$enrichr, database == "NCI-60_Cancer_Cell_Lines")
  
  Table_DT(filtered, colNames = c("Database", "Term", "P-Value", "Adjusted P-Value", "Z-Score", "EnrichR Score", "Involved Genes"), bRownames = FALSE, style = "default", class = "display", 
           dom = "flrtip", alignment = list(centre = NULL, justify = NULL, left = NULL), 
           formatCurr = NULL, formatPerc = NULL, formatRoun = list("cols" = c(3,4,5,6), "digits" = 4), buttons = c('copy', 'csv', 'excel', 'pdf', 'print'), bResponsive = FALSE,
           pageLen = 5, bScroll = FALSE, filename = "GeneSetEnrichment_NCI-60_Cancer_Cell_Lines" )
```


















```{r}
counter <- counter + 1
```







