<!-- 
save as 'sqFastQqcChild'
child of 'screenQuality.Rmd'
--> 



<!--FastQ Quality Plots-->

# FastQ Quality

For FastQ quality control the Bioconductor package [Rqc](https://www.bioconductor.org/packages/release/bioc/html/Rqc.html) was used.
The following sections show several visualizations use to estimate sequencing quality.


## Cycle specific GC Content

This line plot shows the average GC content for each sequencing cycle. It can show a GC content bias.

```{r}
if( extractedFiles$rqc == "" ){
  "No Fastq.gz files uploaded or an error occured during FASTQ analysis."
} else print(extractedFiles$rqc[["GCcontent"]])
```

## Cycle specific Quality Distribution

The bar plot shows the proportion of quality calls per cycle. Colors are presented in a gradient Red-Blue, where red identifies calls of lower quality.

```{r}
if( extractedFiles$rqc == "" ){
  "No Fastq.gz files uploaded or an error occured during FASTQ analysis."
} else print(extractedFiles$rqc[["cycleqcmap"]])
```

## Cycle specific Average Quality

This describes the average quality scores for each cycle of sequencing. 

```{r}
if( extractedFiles$rqc == "" ){
  "No Fastq.gz files uploaded or an error occured during FASTQ analysis."
} else print(extractedFiles$rqc[["QCcycle"]])
```

```{r}
if( extractedFiles$rqc == "" ){
  "No Fastq.gz files uploaded or an error occured during FASTQ analysis."
} else print(extractedFiles$rqc[["AverageQualityPlot"]])
```

```{r}
if( extractedFiles$rqc == "" ){
  "No Fastq.gz files uploaded or an error occured during FASTQ analysis."
} else print(extractedFiles$rqc[["ReadQualityPlot"]])
```

## Cycle specific Base Call Proportion

These bar/line plots describe the proportion of each nucleotide called for every cycle of sequencing. 

```{r}
if( extractedFiles$rqc == "" ){
  "No Fastq.gz files uploaded or an error occured during FASTQ analysis."
} else print(extractedFiles$rqc[["CycleBasecall"]])
```

```{r}
if( extractedFiles$rqc == "" ){
  "No Fastq.gz files uploaded or an error occured during FASTQ analysis."
} else print(extractedFiles$rqc[["CycleBasecallLine"]])
```

## Read Frequency

This plot shows the proportion of reads that appeared many times. 

```{r}
if( extractedFiles$rqc == "" ){
  "No Fastq.gz files uploaded or an error occured during FASTQ analysis."
} else print(extractedFiles$rqc[["ReadFrequency"]])
```

## Read Width

This is a barplot that presents the distribuition of the lengths of the reads available in the FASTQ file. 

```{r}
if( extractedFiles$rqc == "" ){
  "No Fastq.gz files uploaded or an error occured during FASTQ analysis."
} else print(extractedFiles$rqc[["Width"]])
```






